Benchmark!!1

### 2021-01-25 paper/main.tex
a bit more on the paper: description of Or-opt and LNS benchmarks

\subsection{2-opt}
One of the most commonly used heuristics in vehicle routing, 2-opt
improves a tour by performing 2-exchanges. A 2-exchange consists in
removing two edges from a tour and reconnecting the tour with two
other edges. It is equivalent to inverting a sub-sequence of the
tour, and can be performed in place using an array or vector solution
representation.

The checksum for a given permutation seed is calculated as the number of
improvements found while applying first-improvement 2-opt, using this
permutation as starting solution.

\subsection{Or-opt}

The checksum for a given permutation seed is calculated as the number of
improvements found while applying first-improvement Or-opt, using this
permutation as starting solution.

\subsection{Large neighbourhood search}

Note: we use a vector and not a set to store unplanned requests,
otherwise we take the risk of losing determinism.

>>>>

\subsection{2-opt}
The 2-opt heuristic was first described by~\cite{2-opt}.
One of the most commonly used heuristics in vehicle routing, 2-opt
improves a tour by performing 2-exchanges. A 2-exchange consists in
removing two edges from a tour and reconnecting the tour with two
other edges. It is equivalent to inverting a sub-sequence of the
tour, and can be performed in place using an array or vector solution
representation. If the distances are symmetric, then each move can be
evaluated in constant time.

The checksum for a given permutation seed is calculated as the number of
improvements found while applying first-improvement 2-opt until no
improving move exists, using this permutation as starting solution.

\subsection{Or-opt}
Or-opt is a heuristic that was first introduced by~\cite(Or-opt}.
It relies on the exploration of a neighborhood that is a subset of all
3-exchanges. A 3-exchange consists in removing 3 edges from a tour and
reconnecting the tour in a different way. Of all these moves, Or-opt
only considers those that shift a sequence of 1, 2 or 3 vertices to a
different position in the tour. Each move can be evaluated in constant time.

The checksum for a given permutation seed is calculated as the number of
improvements found while applying first-improvement Or-opt until no
improving move exists, using this permutation as starting solution.

\subsection{Large neighbourhood search}
Large neighborhood search (LNS) was originally introduced in
conjunction with constraint programming to solve the vehicle routing
problem with time windows (VRPTW)~\cite{lns}. Since it has been
a very popular method for tackling a wide variety of vehicle routing
problems, see e.g.~\cite{lnschapter}.

LNS iteratively (i) copies the \emph{incumbent} solution, (ii)
destroys the copy by removing some vertices from it, (iii) repairs the
partial solution by re-inserting previously removed customers in it
and (iv) determines whether this newly produced solution becomes the
new incumbent solution or not. The whole method relies, among other
things, on randomness. This is an issue since we want each benchmark
to be deterministic. To remedy this issue, we design deterministic
schemes for both destroying and repairing stages. For each starting
seed, we apply a certain number of LNS iterations. At each iteration,
the vertices at even indices in the tour are removed. These removed
vertices are stored in a vector in the order in which they were
removed, i.e. from smallest to largest index. Then the cost of each
possible insertion is calculated and the cheapest insertion is
performed. Because removed vertices are stored in a vector, the
algorithm's behaviour in case of same-cost insertions is
deterministic.
